\appendices
%
% If you only have one appendix, you should change the above to:
%\appendix
%

\chapter{MORE INFORMATION ON EQUATIONS}

To demonstrate how an appendix should be inserted into the thesis we
have provided two appendices. This first appendix illustrates some
more advanced techniques to improve the appearance of your equations.
Below is a system of partial differential equations from a model for
cellular control by an external nutrient. The equations are
complicated and \LaTeX\ tends to allow them to run into each other. To
prevent this we have used the \verb+\vrule+ command to separate
them. Note this is an ordinary \TeX\ command and is not in L.\
Lamport's book \cite{LAM}. Furthermore, we have some complicated
boundary conditions that we needed to align, so we used the array
command, but to get the equations looking right we also needed the
\verb+\dfrac+ command instead of the \verb+\frac+ command. The
equations for our model are as follows:
\begin{eqnarray}
  \dot{U}_1(t) & = & \tilde f(W_1(t-T)) - U_1(t) + \gamma_1U_2(R\sigma,
   t){\vrule width 0in depth .1in},	\nonumber \\
  \dot{W}_1(t) & = & -\hat b_3W_1(t) + \gamma_3W_2(R\sigma,
   t){\vrule width 0in depth .1in},\nonumber \\
  \frac{\partial U_2}{\partial t} & = & D_1\nabla^2U_2 - U_2 - \tilde f(W_1
    (t-T)) - \gamma_1U_2(R\sigma,t){\vrule width 0in depth .1in},
	\label{sys2} \\
  \frac{\partial V_2}{\partial t} & = & D_2\nabla^2V_2 - b_2V_2 + c_0
    \bigl(U_2 + U_1(t)\bigr){\vrule width 0in depth .1in}, \nonumber \\
  \frac{\partial W_2}{\partial t} & = & D_3\nabla^2W_2 - b_3W_2 + (\hat b_3
    -b_3)W_1 - \gamma_3W_2(R\sigma,t) \nonumber \\
    &  & + k\left[\left[{\left(\frac{D_3}{r^2}\right)}\frac{d}{dr}\left(r^2
	   \frac{dh}{dr}\right) - b_3h\right]V_2(R,t) - h\dot V_2(R,t)
	   \right], \nonumber
\end{eqnarray}
for $t > 0$ and $R\sigma < r < R$ and with the boundary conditions:
\begin{equation*}
\begin{array}{rclcrcl}
 \dfrac{\partial U_2(R\sigma,t)}{\partial r} & = &
   \beta_1U_2(R\sigma,t), & \qquad &
 \dfrac{\partial U_2(R,t)}{\partial r} & = &
   0, \\
\\
 \dfrac{\partial V_2(R\sigma,t)}{\partial r} & = &
   0, & \qquad &
 \dfrac{\partial V_2(R,t)}{\partial r} & = &
   0, \\
\\
 \dfrac{\partial W_2(R\sigma,t)}{\partial r} & = &
   \beta_3W_2(R\sigma,t), & \qquad &
 \dfrac{\partial W_2(R,t)}{\partial r} & = &
   0.
\end{array}
\end{equation*}
Notice that the system is numbered only once by (\ref{sys2}) and that
this is centered as best we can on one line. All other lines have the
$\backslash$\textit{nonumber} command.


\chapter{LISTS AND QUOTATIONS}

The thesis will rarely use list environments, but they are valuable
for r{\'e}sum{\'e}s. For more information on creating a r{\'e}sum{\'e}
you may want to see the author of this document (you also need to
learn quite a bit about \verb+\parbox+ commands).  To create a list
you will want to use one of \texttt{itemize, enumerate,} or
\texttt{description}. For example:
\begin{description}
\item[continuous] A function $f$ is {\bf continuous} at $x$ if and only
if for every $\varepsilon >0$ there exists a $\delta(x) >0$ such that
whenever $|y-x|<\delta$, $|f(y)-f(x)| < \varepsilon$.
\item[uniformily continuous] A function $f$ is {\bf uniformly
continuous} if and only if for every $\varepsilon >0$ there exists a
$\delta >0$ such that whenever $|y-x|<\delta$, $|f(y)-f(x)| <
\varepsilon$ independent of $x$ and $y$.
\item[equicontinuous] A family of functions $f_n$ is {\bf
equicontinuous} at a point $x$ if and only if for every $\varepsilon >0$
there exists a $\delta >0$ such that whenever $|y-x|<\delta$,
$|f_n(y)-f_n(x)| < \varepsilon$ for all functions $f_n$.
\end{description}

\LaTeX\ provides an environment for block quotations. To agree with standard 
thesis formatting manual follow the format below for a quotation exceeding four
lines. From Lewis Carrol's {\it Hunting of the Snark} we hear the
Bellman tell his crew:
 \vspace{.12pt}

{
\ssp
\begin{verse}
The Bellman himself they all praised to the skies--\\
Such a carriage, such ease and such grace!\\
Such solemnity, too! One could see he was wise,\\
The moment one looked in his face!\\
 \vspace{.15in}
He had bought a large map representing the sea,\\
Without the least vestige of land:\\
And the crew were much pleased when they found it to be\\
A map they could all understand.\\
 \vspace{.15in}
``What's the good of Mercator's, North Poles and Equators,\\
Tropics, Zones, and Meridian Lines?''\\
So the Bellman would cry: and the crew would reply,\\
``They are merely conventional signs!''\\
 \vspace{.15in}
``Other maps are such shapes, with their islands and capes!\\
But we've got our brave Captain to thank''\\
(So the crew would protest) ``that he's bought us the best--\\
A perfect and absolute blank!''\\
\end{verse}
}

